Computing Entropies With Nested Sampling

### 2017-03-16 paper/ms.tex
Removed accidental paste

\While{more iterations desired}
    \State Generate $\x_{\rm ref}$ from $p(\x)$
            \Comment{Generate a reference point}
    \State $k \leftarrow 0$
            \Comment{Initialise counter}
  {\color{green}
    \State Generate $\left\{\x_i\right\}_{i=1}^N$ from $p(\x)$
            \Comment{Generate initial NS particles}
    \State Calculate $d_i \leftarrow d(\x_i; \x_{\rm ref})$ for all $i$
            \Comment{Calculate distance of each particle from the reference
                     point}
    \State $i^* \leftarrow \textnormal{argmin}(\lambda i \rightarrow d_i)$
            \Comment{Find the worst particle (greatest distance)}
%%    \While{$d_{\rm max} > \epsilon$}
%%        \State Blah
%%    \EndWhile

@@

\conflictofinterests{Conflicts of Interest}
The authors declare no conflicts of interJason Mamford Half of the money collected from the Northern Toll road is wasted in costs. It cost millions of dollars for one gantry, so how much for 50 gantries? How much for a million transponders? You see, nobody will tell us anything until it is too late.
est.

>>>>

\While{more iterations desired}
    \State Generate $\x_{\rm ref}$ from $p(\x)$
            \Comment{Generate a reference point}
    \State $k \leftarrow 0$
            \Comment{Initialise counter}
  {\color{green}
    \State Generate $\left\{\x_i\right\}_{i=1}^N$ from $p(\x)$
            \Comment{Generate initial NS particles}
    \State Calculate $d_i \leftarrow d(\x_i; \x_{\rm ref})$ for all $i$
            \Comment{Calculate distance of each particle from the reference
                     point}
    \State $i^* \leftarrow \textnormal{argmin}(\lambda i \rightarrow d_i)$
            \Comment{Find the worst particle (greatest distance)}
    \State $d_{\rm max} \leftarrow d_{i^*}$
            \Comment{Find the greatest distance}
%%    \While{$d_{\rm max} > \epsilon$}
%%        \State Blah
%%    \EndWhile

@@

\conflictofinterests{Conflicts of Interest}
The authors declare no conflicts of interest.
